Designing a Search for the BBC

### 2013-08-26 coursework.tex
Done most design. Analysis and evaluation to follow.

In the specific example of television programming, we need to maintain
systems thinking throughout the design process to ensure that we
create a search application that both meets the needs of the public
using the application to search for programmes and forms part of
a television production and delivery system that itself meets the
needs of the television-watching public. It is not always the case
that the holistic system will behave predictably from the behaviours
of its parts.

@@

@enduml
\end{comment}
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_producer.png}
  \end{center}
  \caption{Sequence diagram showing publication of programme information to the search indexes\label{sequence-producer}}
\end{figure}

@@

@enduml
\end{comment}
\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_user.png}
  \end{center}
  \caption{Sequence diagram showing a user interacting with search\label{sequence-user}}
\end{sidewaysfigure}

@@

\section{Domain Model}
\begin{comment}
@startuml model.png

skinparam monochrome true
skinparam circledCharacterRadius 0
skinparam circledCharacterFontSize 0
skinparam classFontSize 20

class CreativeWork
class NewsItem extends CreativeWork
class Programme extends CreativeWork
class BlogPost extends CreativeWork
class LiveCoverage extends CreativeWork
class LiveEventPage extends CreativeWork

class Thing
class Person extends Thing
class Event extends Thing
class Place extends Thing
@enduml
\end{comment}

\chapter{Analysis}

>>>>

In the specific example of television programming, we need to maintain
systems thinking throughout the design process to ensure that we
create a search application that both meets the needs of the public
using the application to search for programmes and forms part of
a television production and delivery system that itself meets the
needs of the television-watching public.

@@

@enduml
\end{comment}
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_producer.png}
  \end{center}
  \caption{Sequence diagram showing publication of programme information to the search indexes\label{sequence-producer}}
\end{figure}

@@

@enduml
\end{comment}
\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_user.png}
  \end{center}
  \caption{Sequence diagram showing a user interacting with search\label{sequence-user}}
\end{figure}

@@

One solution to this in modern web application design is to
push the lazy loading into the web browser using AJAX. \cite{garrett2005ajax}
Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
this still requires just as many calls to backend services --
perhaps even more complexity as the calls are going through
more layers -- it can give a user experience than appears more responsive.

Preparing a search results page with minimal information that is then
augmented asynchronously is a user experience technique that gives the
illusion of lower latency; the additional information can update the page
during the user's reaction time in the best case. This is an important
aspect of user experience to get right as multivariate testing at Google
in 2006 showed that an additional 500ms of latency dropped traffic
and revenue by 20\%. \cite{linden2006marissa}

\begin{comment}
@startuml sequence_ajax.png

    search --> www : Return stub items
    deactivate search

    www --> User : search results page

    note over www
      Website remains active using Javascript to do 
      AJAX requests for further information for
      each result.
    end note

    loop for each item
      www ->> search : Fetch more info about item
      activate search
      search -> source : Proxy to source for info
      activate source
      source --> search : Return info in source's own format
      deactivate source
      search --> www : Return info in common format
      deactivate search
      www --> User : Update page in front of user as info arrives
    end

deactivate www

@enduml
\end{comment}
\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_ajax.png}
  \end{center}
  \caption{Sequence diagram showing rich information lazy-loaded via AJAX\label{sequence-ajax}}
\end{figure}

\section{Domain Model}

It has been expressed already that a BBC-wide search application
is going to have to index, retrieve and display a diverse set of
information. Parts of the application might well want to incorporate
a domain model \cite{fowler2002patterns} so as to understand how
to perform each of these actions against each possible item
the search application could return as a search result. A maximal
model is shown in figure~\ref{model} that attempts to capture
a good proportion of the content and concepts the BBC has
been attempting to model over several years. This model is
an aggregate of individual ontologies developed for specific purposes,
but given the search application has to provide the discovery for
the full set of this information, it is not unreasonable that
a search application would have a domain model that covers the totality.

Note that complexity of information for programmes alone. \cite{raimond2009bbc}
A programme to a member of the public could actually refer to an
exact episode or indeed the \emph{brand}, i.e. the title that
persists to all episodes. An example of a brand would be
\emph{Doctor Who}, which itself contains multiple series, which in turn
contain a collection of episodes. Note that the brand itself has episodes
as immediate children that do not live under a series, e.g. Christmas specials.
It is also the case that certain things do not have brands or series, e.g.
a film is modelled as a one-off episode.

This leads to some difficult questions for a search application. If a user
searches for the text ``doctor who'', are they expecting a link to the
latest episode to watch on iPlayer, information about the next episode
-- such as when it is due to be broadcast -- or a link to the overall
home page for the entire Doctor Who brand?

The model also skims the surface of the sport ontology \cite{rayfield2011bbc}
created before the 2012 Olympic games, which aims to model the whole domain
of sporting personalities, events and competitions (and more). This might
be too fine-grained for the domain model used within the search application,
but it is likely that people will want to search for competitions like
``World Cup'' or sporting disciplines such as ``football''. A search application
that understands these concepts as entities in their own right may well
be able to direct users at a curated, dedicated ``home page'' thereof alongside
simply matching articles and other works that contain those terms only.

\begin{comment}
@startuml model.png

skinparam monochrome true
skinparam circledCharacterRadius 0
skinparam circledCharacterFontSize 0

package CreativeWorks {
class CreativeWork {
  title : String
  dateModified : DateTime
  dateCreated : DateTime
  category : String
  description : String
  thumbnail: Image
}
class NewsItem extends CreativeWork
class BlogPost extends CreativeWork
class LiveCoverage extends CreativeWork
class LiveEventPage extends CreativeWork

interface Format
class TextualFormat extends Format
class VideoFormat extends Format
class InteractiveFormat extends Format
class ImageFormat extends Format
class AudioFormat extends Format
class PictureGalleryFormat extends Format
}

package Programmes {
class Programme
Programme <|-r- CreativeWork
class Brand extends Programme
class Series extends Programme
class Episode extends Programme

class Service
class Version
class Broadcast
class Ondemand
}

Service "1" -- "0..n" Programme : masterBrand
Episode "1" *-- "0..n" Version : hasVersions

Version "1" -- "0..n" Broadcast : broadcasts
Version "1" -- "0..n" Ondemand : availableOndemandWindows

Broadcast "1..n" -- "1" Service : broadcastOn
Ondemand "1..n" -- "1" Service : availableOn

Brand "1" *-r- "0..n" Series
Series "1" *-d- "0..n" Series
Series "1" *-r- "0..n" Episode

package Concepts {
class WebDocument
class Thing {
  preferredLabel
}
class Person extends Thing
class Event extends Thing
class Place extends Thing
class Theme extends Thing
class Organisation extends Thing
}

CreativeWork "1" -- "1..2" WebDocument : primaryContent
Thing "1" -- "0..n" WebDocument : primaryTopic
CreativeWork "0..n" -- "1" Format : primaryFormat
CreativeWork "0..n" -- "0..n" Thing : tag
Thing "0..n" -- "0..n" Thing : notablyAssociatedWith

package Sport {
class SportCompetition extends Event
class SportDiscipline extends Thing
}

Event "0..n" -- "0..n" Programme : coverage
SportCompetition "0..n" -- "0..n" Person : competesIn
SportDiscipline "1" -- "0..n" SportCompetition

@enduml
\end{comment}
\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{model.png}
  \end{center}
  \caption{Domain model for content items and other things pertinent to BBC contenet\label{model}}
\end{sidewaysfigure}

\chapter{Analysis}
\label{analysis}
